Manuscript for MADA Project

### 2024-03-14 products/manuscript/Manuscript.qmd
Updated Manuscript
Added models of interest

  ** WILL BE PERFORMED IN THE STATISTICAL ANALYSIS FILE **

>>>>

We'll begin to look at some of the relationships between our variables now. Sleep Quality is our outcome of interest for all of these. We'll start with Phyiscal Activity level.

```{r}
############################
#### Fitting a model using Quality of Sleep as the outcome and Physical Activity Level as a predictor

lmfit_quality_activity <- lm(Quality.of.Sleep ~ Physical.Activity.Level, sleepdata)

# Placing results from lmfit_quality_activty  into a data frame with the tidy function
lmtable_quality_activity <- broom::tidy(lmfit_quality_activity)

# Viewing the results from the first model fit 
print(lmtable_quality_activity)

# Saving the lmfit_quality_activity results table  
lmtable_quality_activity = here("results", "tables", "lmfit1table.rds")
saveRDS(lmtable_quality_activity, file = lmtable_quality_activity)
```

The intercept value indicates that Quality of Sleep will be 6.66 if physical activity is at 0. This has a relatively low standard error and high significance.The coefficient for our variable indicates that as Physical activity level increases by one unit, Quality of Sleep will increase by 0.0109. Our t-statistic is indicated as significant by the p-value but is much lower than the intercept's.This means that Physical Activity Level does have a measurable impact on Quality of Sleep, but it's relatively small.

Next, we'll look at Sleep Duration as a predictor.

```{r}
############################
#### Fitting a model using Quality of Sleep as the outcome and Sleep Duration as a predictor

lmfit_quality_duration <- lm(Quality.of.Sleep ~ Sleep.Duration, sleepdata)

# Placing results from lmfit_quality_duration into a data frame with the tidy function
lmtable_quality_duration <- broom::tidy(lmfit_quality_duration)

#Viewing the results from the second model fit 
print(lmtable_quality_duration)

# Saving the lmfit_quality_duration results table  
lmtable_quality_duration = here("results", "tables", "lmfit2table.rds")
saveRDS(lmtable_quality_duration, file = lmtable_quality_duration)

For our sleep duration model, we can see that our intercept's negative value indicates that Quality of Sleep would be very poor if individuals got no sleep. This is rational and is supported by a strong p-value and a decent t-statistic, although the standard error is a bit high. For our variable coefficient, we can see that as sleep duration increases by one unit, Quality of sleep also increases by about 1. This has a very strong p-value and t-statistic, indicating a strong relationship between this predictor and our outcome of interest.

Next, we'll look at Stress Level as our predictor.

```{r}
############################
####Fitting a model using Sleep Quality as the outcome and Stress Level as a predictor.

lmfit_quality_stress <- lm(Quality.of.Sleep~ Stress.Level, sleepdata)

#Placing results from lmfit_quality_stress into a data frame with the tidy function
lmtable_quality_stress <- broom::tidy(lmfit_quality_stress)

#Viewing the results from the sixth model fit 
print(lmtable_quality_stress)

# Saving the lmfit_quality_stress results table  
lmtable_quality_stress = here("results", "tables", "lmfit6table.rds")
saveRDS(lmtable_quality_stress, file = lmtable_quality_stress)
```

According to our model, Stress has a strongly defined relationship with sleep quality. We can see that a value of 0 on the stress score leads to a 10 unit increase in quality of sleep. The Stress Level coefficient indicates that as stress increases by one unit, sleep quality decreases by about 0.6 of a unit. The t-statistics and p-values for the values in this model are extremely strong, indicating a well-defined relationship between stress and sleep quality.

Finally, we'll look at Age as our predictor.

```{r}
############################
####Fitting a model using Sleep Quality as the outcome and Age as a predictor.

lmfit_quality_age <- lm(Quality.of.Sleep~ Age, sleepdata)

#Placing results from lmfit_quality_gender_age into a data frame with the tidy function
lmtable_quality_age <- broom::tidy(lmfit_quality_age)

#Viewing the results from the seventh model fit 
print(lmtable_quality_age)

# Saving the lmfit_quality_gender_age results table  
lmtable_quality_age = here("results", "tables", "lmfit8table.rds")
saveRDS(lmtable_quality_age, file = lmtable_quality_age)

Our model shows a strong relationship between age and quality of sleep. As Age increases, sleep quality seems to improve. Each year increase in age is predicted to have a 0.065 increase in sleep quality score. The intercept here is also interesting as an age of "0" is predicted to have a sleep score of 4.57, which is relatively poor. The t-statistics and p-values for these are both strong.
